%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Anirudh} \headerlastnamestyle{Emmadi} \\
	\vspace{2mm}
	{\faEnvelope\ emmadi.anirudh@gmail.com} | {\faMobile\ +1(469)403-1726} | {\faMapMarker\ Little Elm, TX} | {\faLink\ https://anirudhemmadi.com}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Webmaster}
	{Artificial Intelligence Society}
	{UTDallas, Richardson, TX}
	{Jan 2019 – Present}
	{\begin{cvitems}
		\item {Develop and Maintain website for AIS Organization at UTDallas}
		\end{cvitems}}
	\cventry
	{President \& Founder}
	{Application Development Club}
	{Coppell High School, Coppell, TX}
	{Sep 2017 – June 2018}
	{\begin{cvitems}
		\item {Took the initiative to create an app dev club to inspire and guide high schoolers into the world of tech and developement}
		\end{cvitems}}
	\cventry
	{Web Developer}
	{Freelancer}
	{Remote}
	{June 2016 – Oct 2017}
	{\begin{cvitems}
		\item {Developed and maintained websites for clients. Worked with HTML5, CSS3, Bootstrap, Javascript, nodeJS, and jQuery.}
		\end{cvitems}}
\end{cventries}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Languages:  & {\skill{ Java, C++, JavaScript (ES6), HTML, CSS}} \\
		Frameworks/Libraries:  & {\skill{ NodeJS, ReactJS, React-Native, jQuery, Bootstrap}} \\
		Databases:  & {\skill{ MongoDB, NoSQL, Firebase}} \\
		Miscellaneous:  & {\skill{ Git + Github, Linux Command Line, Markdown, JSON, API Calling}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{A food delivery service for students, by students. A mobile application tailored specifically for restaurants, and food courts located in college campuses.}
	{DormDash}
	{React-Native, JavaScript, NoSQL}
	{http://dormdashapp.com}
	{}
	
	\vspace{-5mm}
	\cventry
	{A multi-purpose discord bot that does everything from getting user game stats to displaying memes.}
	{KannaBot}
	{nodeJS, discordJS, MongoDB}
	{https://kannabot.ml}
	{}
	
	\vspace{-5mm}
	\cventry
	{An android application that allows users to scan an object and determines whether the object is recyclable or not.}
	{iCycle}
	{Java, Android Studio, Firebase}
	{https://github.com/KannaDev/iCycle}
	{}
	
	\vspace{-5mm}
	\cventry
	{A decentralized cloud storage platform. Made for Proof of Hack Hackathon in 24 hours.}
	{BDrive}
	{React, IPFS, MetaMask}
	{https://github.com/KannaDev/bdrive}
	{}
	
	\vspace{-5mm}
\end{cventries}
\cvsection{Honors \& Awards}
\begin{cvhonors}
	\cvhonor
	{HackUTD Winner \textasciitilde{} Second Place}
	{Presented \& demoed in front of 500+ developers and 119 teams.}
	{HackUTD}
	{Feb 2019}
	\cvhonor
	{GameChangers Hackathon Winner \textasciitilde{} First Place}
	{Best discord bot with tremendous potential.}
	{OP:Live}
	{Sep 2018}
	\cvhonor
	{SevenTablets Hackathon Winner \textasciitilde{} Third Place}
	{First ever hackathon, built my first android application.}
	{SevenTablets}
	{Jan 2018}
\end{cvhonors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Bachelor of Science (BS) in Computer Science}
	{The University Of Texas At Dallas}
	{Richardson, TX}
	{Sep 2018 – May 2022}
	{GPA: 3.8}
	\cventry
	{High School Degree}
	{Coppell High School}
	{Coppell, TX}
	{Aug 2016 – June 2018}
	{GPA: 5.4171}
	\cventry
	{High School Degree}
	{Delhi Public School}
	{Nacharam, Hyderabad, INDIA}
	{June 2014 – April 2016}
	{GPA: 9.2}
\end{cventries}

\vspace{-2mm}
\ 
\end{document}